\documentclass[11pt]{article}
\usepackage{graphicx} % Required for inserting images
\setlength{\parindent}{0pt}
\usepackage[bookmarks=true, colorlinks=true, urlcolor=blue, linkcolor=black]{hyperref}

\usepackage{enumitem}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{geometry}
\usepackage{lastpage}
\usepackage{fancyhdr}
\usepackage{datetime}

% Link to other SOPs, forms
\usepackage{xr}
\externaldocument[101-]{../../100_emergency/1_hardware/sop_101_hardware}
\input{../../def_definitions.tex}

% figures and tables
\usepackage{graphicx}
\graphicspath{ {../../pics} }
\usepackage{rotating}
\usepackage{float}
\usepackage{subfig}
\usepackage{caption}
\DeclareCaptionLabelFormat{adja-page}{\hrulefill\\#1 #2 \emph{(previous page)}}


\renewcommand{\headrulewidth}{0pt}
% \newdateformat{yearmonth}{\THEYEAR-\THEMONTH-\THEDAY}
\pagestyle{fancy}
\fancyhead[L]{}
\fancyhead[R]{Approved: TBD}
\fancyfoot[C]{}
\fancyfoot[L]{ND-HNC SOP 304: v.0.2.0}
\fancyfoot[R]{p. \thepage /\pageref*{LastPage}}


% start document
\begin{document}

\renewcommand{\labelenumii}{\arabic{enumi}.\arabic{enumii}}
\renewcommand{\labelenumiii}{\arabic{enumi}.\arabic{enumii}.\arabic{enumiii}}
\renewcommand{\labelenumiv}{\arabic{enumi}.\arabic{enumii}.\arabic{enumiii}.\arabic{enumiv}}

\begin{center}
	\textbf{\Large SOP 304: Active Violence}\\
	\hrulefill
\end{center}


\section{Summary}
This document establishes  procedures for active violence situations at the Notre Dame Human Neuroimaging Center (ND-HNC), located in the Lower Level of:\\

Veldman Family Psychology Clinic\\
501 North Hill St.\\
South Bend, IN 46617

\section{Scope}
These policies apply to all investigators, research assistants, and staff who use the ND-HNC.

\section{Definitions}

\begin{itemize}
	\item \NDHNC
	\item \VFPC
\end{itemize}

\section{Notes}

None.


\section{Policies \& Procedures}

Procedures for active violence situations are detailed.


% Violence
\subsection{Active Violence is Occurring}
\label{ssec:active-violence}
If you ever find yourself in an active situation, remember ``\textbf{Run, Hide, Fight!}''.

\begin{enumerate}
	\item Run!
	\begin{enumerate}
        \item Get away from the threat, leave your belongings behind.
        \item Save yourself, help others if possible.
        \item Call 911 when safe.
        \item Do \textbf{NOT} congregate.
    \end{enumerate}
	\item Hide!
	\begin{enumerate}
        \item If evacuation is not possible, find a place where the active shooter is less likely to find you.
        \item Within the building, find a room you can lock and barricade yourself inside using any equipment or furniture items.
        \item Silence your cell phone and remain quiet.
        \item Call 911 to alert authorities to the situation and possibly to the active shooter's location.
    \end{enumerate}
    \item Fight!
	\begin{enumerate}
        \item As a last resort and only if your life is in immediate danger.
        \item Disrupt or incapacitate the active shooter by acting as aggressively as you can.
        \item Use any item as a makeshift weapon.
        \item If you are with others, work together to stop the threat.
        \item Whatever you do, commit to your actions.
    \end{enumerate}
\end{enumerate}


% Police response
\subsection{Police Response to Active Violence Situations}
\label{ssec:police}

Be aware: the number one priority for police is to stop the threat quickly. Therefore, police may:

\begin{enumerate}
	\item Arrive in variable attire such as plain clothes or uniforms from other agencies.
	\item Be carrying weapons including rifles.
	\item Shout commands such as ``put your hands up''.
	\item Move past injured persons to locate and stop the active threat.
\end{enumerate}

Always comply with police instruction.


% No Guns
\subsection{No Guns Policy}
\label{ssec:no-guns}

\begin{enumerate}
	\item It is a University firearm policy that weapons are not allowed on Notre Dame property.
	\item If you see someone carrying a firearm, contact the Notre Dame Police Department (NDPD) at (574) 631-5555. NDPD will respond because it is a University firearm policy that is being violated, not a criminal response.
	\item Let the person know weapons are not allowed on Notre Dame property.
	\item Call 911 if anything seems suspicious - don't worry if you should be calling NDPD or South Bend police, just call 911 and get help.
\end{enumerate}


\section{Figures}

None.

\end{document}